Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-06-09 manuscript/supplement.tex
Report effect sizes for bootstrap analyses
Adds mean +/- standard deviation of bootstrap distributions to violin plots of
distributions to better communicate the effect sizes of model improvements over
the naive.

\begin{figure}[H]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/bootstrap_distributions_for_simulated_sample_3.pdf}
  \caption{
  Bootstrap distributions of the mean difference of distances to the future between biologically-informed and naive models for simulated populations.
  Empirical differences in distances to the future were sampled with replacement and mean values for each bootstrap sample were calculated across n=10,000 bootstrap iterations.
  The horizontal gray line indicates a difference of zero between a given model and its corresponding naive model.
  Each model is annotated by the p-value representing the proportion of bootstrap samples with values less than zero (see Methods).
  }
  \label{sup_fig:bootstrap_distributions_for_simulated_sample_3}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding.pdf}
  \caption{
  Bootstrap distributions of the mean difference of distances to the future between biologically-informed and naive models for natural populations.
  Empirical differences in distances to the future were sampled with replacement and mean values for each bootstrap sample were calculated across n=10,000 bootstrap iterations.
  The horizontal gray line indicates a difference of zero between a given model and its corresponding naive model.
  Each model is annotated by the p-value representing the proportion of bootstrap samples with values less than zero (see Methods).
  }
  \label{sup_fig:bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding}
  \end{center}
\end{figure}

>>>>

\begin{figure}[H]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/bootstrap_distributions_for_simulated_sample_3.pdf}
  \caption{
  Bootstrap distributions of the mean difference of distances to the future between biologically-informed and naive models for simulated populations.
  Empirical differences in distances to the future were sampled with replacement and mean values for each bootstrap sample were calculated across n=10,000 bootstrap iterations.
  The horizontal gray line indicates a difference of zero between a given model and its corresponding naive model.
  Each model is annotated by the mean $\pm$ the standard deviation of the bootstrap distribution.
  Models are also annotated by the p-value representing the proportion of bootstrap samples with values less than zero (see Methods).
  }
  \label{sup_fig:bootstrap_distributions_for_simulated_sample_3}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding.pdf}
  \caption{
  Bootstrap distributions of the mean difference of distances to the future between biologically-informed and naive models for natural populations.
  Empirical differences in distances to the future were sampled with replacement and mean values for each bootstrap sample were calculated across n=10,000 bootstrap iterations.
  The horizontal gray line indicates a difference of zero between a given model and its corresponding naive model.
  Each model is annotated by the mean $\pm$ the standard deviation of the bootstrap distribution.
  Models are also annotated by the p-value representing the proportion of bootstrap samples with values less than zero (see Methods).
  }
  \label{sup_fig:bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding}
  \end{center}
\end{figure}

### 2020-06-09 manuscript/tables/composite_vs_individual_model_comparison.tex
Report effect sizes for bootstrap analyses
Adds mean +/- standard deviation of bootstrap distributions to violin plots of
distributions to better communicate the effect sizes of model improvements over
the naive.

\begin{tabular}{llllrr}
\toprule
    sample &  error\_type &      individual\_model &                         composite\_model &  empirical\_difference &  p\_value \\
\midrule
 simulated &  validation &          true fitness &                  mutational load +  LBI &                  0.42 &   0.9672 \\
 simulated &  validation &       mutational load &                  mutational load +  LBI &                 -1.03 &   0.0000 \\
 simulated &  validation &                   LBI &                  mutational load +  LBI &                 -0.33 &   0.0097 \\
 simulated &        test &          true fitness &                  mutational load +  LBI &                 -0.28 &   0.1395 \\
 simulated &        test &       mutational load &                  mutational load +  LBI &                 -1.11 &   0.0000 \\
 simulated &        test &                   LBI &                  mutational load +  LBI &                 -0.41 &   0.0001 \\
   natural &  validation &       mutational load &                  mutational load +  LBI &                 -0.69 &   0.0034 \\
   natural &  validation &                   LBI &                  mutational load +  LBI &                 -0.23 &   0.0026 \\
   natural &  validation &       mutational load &  mutational load + HI antigenic novelty &                 -0.31 &   0.0420 \\
   natural &  validation &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.18 &   0.0560 \\
   natural &        test &       mutational load &                  mutational load +  LBI &                  1.17 &   0.9379 \\
   natural &        test &                   LBI &                  mutational load +  LBI &                 -0.70 &   0.0000 \\
   natural &        test &       mutational load &  mutational load + HI antigenic novelty &                 -0.56 &   0.0113 \\
   natural &        test &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.24 &   0.0962 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llllrr}
\toprule
    sample &  error\_type &      individual\_model &                         composite\_model &  empirical\_difference &  p\_value \\
\midrule
 simulated &  validation &          true fitness &                  mutational load +  LBI &                  0.42 &   0.9670 \\
 simulated &  validation &       mutational load &                  mutational load +  LBI &                 -1.03 &   0.0000 \\
 simulated &  validation &                   LBI &                  mutational load +  LBI &                 -0.33 &   0.0098 \\
 simulated &        test &          true fitness &                  mutational load +  LBI &                 -0.28 &   0.1391 \\
 simulated &        test &       mutational load &                  mutational load +  LBI &                 -1.11 &   0.0000 \\
 simulated &        test &                   LBI &                  mutational load +  LBI &                 -0.41 &   0.0001 \\
   natural &  validation &       mutational load &                  mutational load +  LBI &                 -0.69 &   0.0028 \\
   natural &  validation &                   LBI &                  mutational load +  LBI &                 -0.23 &   0.0037 \\
   natural &  validation &       mutational load &  mutational load + HI antigenic novelty &                 -0.31 &   0.0396 \\
   natural &  validation &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.18 &   0.0534 \\
   natural &        test &       mutational load &                  mutational load +  LBI &                  1.17 &   0.9365 \\
   natural &        test &                   LBI &                  mutational load +  LBI &                 -0.70 &   0.0000 \\
   natural &        test &       mutational load &  mutational load + HI antigenic novelty &                 -0.56 &   0.0133 \\
   natural &        test &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.24 &   0.0965 \\
\bottomrule
\end{tabular}
